{\acronym} meets FOX: a combined approach to entity linking based on vector similarity

### 2015-08-20 paper.tex
- added a table for the results with reduced component sets. Still waiting on some results to fill in some data points.

\usepackage{lipsum}
\usepackage{todonotes}
\usepackage{booktabs}
\usepackage{tabularx}
\newcolumntype{Y}{>{\centering\arraybackslash}X}

@@

>>>>

\usepackage{lipsum}
\usepackage{todonotes}
\usepackage{booktabs}
\usepackage{tabularx}
\newcolumntype{Y}{>{\centering\arraybackslash}X}
\newcolumntype{s}{>{\hsize=2\hsize}X}

@@

\begin{table}[t]
\begin{center}
\begin{tabularx}{\textwidth}{ X Y Y Y Y Y Y}
\toprule
& \multicolumn{3}{c}{AIDA/CoNLL}  
& \multicolumn{3}{c}{KORE50}\\
\cmidrule(lr){2-4} \cmidrule(lr){5-7}
 & Precision & Recall & $F_1$ & Precision & Recall & $F_1$ \\ 
\midrule
\emph{without} &  &  &  &  &  &  \\ 
SNS & x & x & x & 0.32 & 0.28 &  0.29 \\
tf-idf & x & x & x & 0.32 & 0.28 &  0.29 \\
page rank & x & x & x & 0.12 & 0.10 &  0.11 \\
CRP & x & x & x & 0.31 & 0.27 & 0.29 \\
\midrule
\emph{only with} &  &  &  &  &  &  \\ 
SNS & x & x & x & 0.07 & 0.06 &  0.06 \\
tf-idf & x & x & x & 0.08 & 0.07 &  0.07 \\
page rank & x & x & x & 0.32 & 0.28 &  0.29 \\
CRP & x & x & x & 0.08 & 0.07 &  0.07 \\
\bottomrule
\end{tabularx}
\end{center}
\caption{Results for the AIDA/CoNLL and KORE50 datasets when one of the components is removed and when only one component is used for classification. SNS is Semantic Neighborhood Signature Vector Similarity, CRP is Candidate Reference Probability.}
\label{table:components}
\end{table}
